---
title: "Lab3"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab3}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753GALEXFLAB3)
```

# ggmytable

The "ggmytable" function takes a data frame, denoted as df, along with 2 qualitative and 1 quantitative variables (x,y, and z respectively) to produce a bar graph. Here, the x value designates the x axis, count is shown for the y axis, and the y variable designates how the graph is wrapped. Additionally, a summary is produced, grouped by the y variable, that determines the mean of z and the count with n.

Overall, the lab serves to practically apply prior knowledge surrounding making functions, along with data wrangling and graphing via ggplot, to develop packages providing a beneficial tool towards analyzing data. 

```{r}
MATH4753GALEXFLAB3::ggmytable(ddt,"SPECIES","RIVER", "LENGTH")
```

